Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-06-09 WSSSPE1_report/WSSSPE1_summary_report.tex
Added some references to relevant papers discussing training
I think these papers sufficiently elaborate on the points made here.

\subsection{Training Scientists to Develop and Support Software}
Part of the panel discussion focused around community structures and
how academic communities are not taught how to evaluate
cross-disciplinary work.  One question raised was whether software
developers can be effective if they are not part of the appropriate
domain community, with responses that this depends on the specific
problem and situation, and that ``T-shaped'' people who have both
disciplinary depth as well as interdisciplinary and collaboration
skills are important.  The discussion focused on whether we could
teach software developers and domain scientists to collaborate
together more effectively rather than trying to teach software
developers about domain science and domain scientists about software
development practices.  The end goal of this would be to have a single
community with a spectrum of expertise across domain science and
software development rather than two separate communities.

The role of the growing field of team science with software
development was discussed. Team science deals with understanding and
improving collaborative and team-based scientific research, and issues
such as virtual organizations, and tool development across software
development communities. Further, how should these skills and best
practices then be introduced to students?

>>>>

\subsection{Training Scientists to Develop and Support Software}

Part of the panel discussion focused around community structures and
how academic communities are not taught how to evaluate
cross-disciplinary work. One question raised was whether software
developers can be effective if they are not part of the appropriate
domain community, with responses that this depends on the specific
problem and situation, and that ``T-shaped'' people who have both
disciplinary depth as well as interdisciplinary and collaboration
skills are important~\cite{Trainer_WSSSPE, Dubey_WSSSPE, Girotto_WSSSPE}.
The discussion focused on whether we could
teach software developers and domain scientists to collaborate
together more effectively rather than trying to teach software
developers about domain science and domain scientists about software
development practices. The end goal of this would be to have a single
community with a spectrum of expertise across domain science and
software development, rather than two separate communities~\cite{Prlic_WSSSPE}.

The role of the growing field of team science with software
development was discussed. Team science deals with understanding and
improving collaborative and team-based scientific research, and issues
such as virtual organizations, and tool development across software
development communities~\cite{Christopherson_WSSSPE, Cranston_WSSSPE}.
Further, how should these skills and best practices then be introduced to students?
